\singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}

### 2022-01-27 Manuscript/Lanuza_et_al_2021_Ecol_Letters.tex
edits

All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} n.d.}) version \emph{0.9.99}. We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.

@@

\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (n.d.). Taxize: {Taxonomic} information from around the web. R package version 0.9.99 (2020).~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.

>>>>

All species names, genera, families and orders were retrieved and standardized from the taxonomy data sources NCBI (\url{https://www.ncbi.nlm.nih.gov/taxonomy}) for plants and ITIS (\url{https://www.itis.gov/}) for pollinators, using the R package \emph{taxize} (\protect\hyperlink{ref-chamberlain2020}{Chamberlain \emph{et al.} 2020}) version \emph{0.9.99}. We filled the `not found' searches manually using \url{http://www.theplantlist.org/} and \url{http://www.mobot.org/} for plants and \url{http://www.catalogueoflife.org/} for floral visitors.

@@

\leavevmode\vadjust pre{\hypertarget{ref-chamberlain2020}{}}%
Chamberlain, S., Szoecs, E., Foster, Z., Arendsee, Z., Boettiger, C., Ram, K., \emph{et al.} (2020). Taxize: {Taxonomic} information from around the web. R package version 0.9.99.~At \href{https://CRAN.R-project.org/package=taxize}{https://CRAN.r-project.org/package=taxize}.

### 2022-01-27 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Nat_Eco_Evo.Rmd
edits for Ecol Letters
edits

\renewcommand{\figurename}{}

```{r echo=FALSE, out.width='100%', fig.align='center'}
knitr::include_graphics('../Images/pnas-logo.png')
```

@@

#Images were made by Paula Martin

@@

  plot <- plot + geom_point(data=dat, aes(x, y),size=0.95, color="black")

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

>>>>

@@

#Images were made by Paula Martin
PC$S[,1] <- -PC$S[,1]

@@

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,4.8,4.8,5.5,5,5.5,5.8,6.5)), y = -(PCAloadings$PC2*c(4.8,4.4,4.15,5.35,5,4.7,5.75,6)+c(0,0,0,0,0,0,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
